% Abel's resume
% Accurate as of: Jan 14th 2022

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{tabularx}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}

\usepackage[charter]{mathdesign} % Bitstream Charter
% \usepackage{newpxtext,newpxmath} % Palatino

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{table}[]
    \begin{tabularx}{\textwidth}{Xr}
        \Huge{Abel Salau}
        &
        \begin{tabular}[c]{@{}r@{}}
            \href{mailto:asalau54@gmail.com}{\texttt{asalau54@gmail.com}} \\
            \href{tel:+16475705455}{\texttt{(647) 570 5455}} \\
            \href{https://abel-salau.github.io}{\texttt{abel-salau.github.io}} \\
        \end{tabular}
    \end{tabularx}
\end{table}

%-----------SKILLS-----------------
\shorterSection{Technical Skills}
  \resumeSubHeadingListStart
  \small
    \item{
        \textbf{Languages}{: Scheme, Python, C, R, SQL}
    } \vspace{-5pt}

     \vspace{-5pt}

    \item{
        \textbf{Tools/Environments}{: Power BI, Microsoft Excel, Google Workspace, IDEs, VSCode, RStudio, Git}
    }

\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\shorterSection{Professional Experience }
 \resumeSubHeadingListStart
 
    \resumeSubheading
      {Backpacker College}{Waterloo, ON}
      {System Administrator}{September 2021 - Present}
      \resumeItemListStart
         \resumeItem{Large-Scale System Management}{Tasked to continuously improve and maintain digital curated Backpacker College content within new and established systems.}
         \resumeItem{Automation and Integration}{ Responsible for building over 25 listings weekly and creating automation scripts to streamline their integration with partner platforms such as Guesty, AirBnB, TripAdvisor and VRBO.}
         \resumeItem{Customer Correspondence}{Involved in the interaction and fulfilment of bookings with potential backpackers and room providers alike.}
      \resumeItemListEnd

    \resumeSubheading
    {Rise in STEM}{Toronto, ON}
    {Research and Evaluation Assistant} {August 2021 - Present}
    \resumeItemListStart
        \resumeItem{Data Collation}{Responsible for research and data collation on delegated projects.}
        \resumeItem{Membership Support}{Providing support for general members transition into post-secondary and the workforce.}
        \resumeItem{Personnel Management}{Responsible for connecting general members to our community networks and various provided support systems in a fast-paced startup environment.}
    \resumeItemListEnd

    

  \resumeSubHeadingListEnd
  
  %-----------PROJECTS-----------------
\shorterSection{Projects}
  \resumeSubHeadingListStart
     \resumeSubItem{\href{https://github.com/abel-salau/happy-x-covid}{Population Data Exploration}}
     {Created data-set from multiple sources on COVID-19 and general population data \\
     \emph{Python (NumPy, Pandas, BeautifulSoup4, Sklearn,)}
        \vspace{-5pt}
        \begin{itemize}
            \item Ranked countries based on their happiness index gotten from the 2021 World Happiness Report.
            \item Webscrapped through dynamic sites/databases to get real-time updates on recorded COVID-19 statistics.
            \item Cleaned up data from all sources to only include relevant information in the resulting data-set.
        \end{itemize}
     }
  \resumeSubItem{\href{https://github.com/abel-salau/fin.dash}{Personal Finance Dashboard}}
  {Visualization of inputted monetary data \\
      \emph{Excel (Pivot tables, Formulas), Power BI (Queries)}
        \vspace{-5pt}
        \begin{itemize}
            \item Designed an interactive, customizable dashboard to visualize income, spending and budget on a month to month basis.
            \item Integrated a separate simple excel worksheet to make data insertion intuitive.
            \item Implemented a minimalist design that highlights only the most important data first.
        \end{itemize}
     }
  \resumeSubHeadingListEnd
 

%-----------VOLUNTEERING-----------------
\shorterSection{Volunteer Experience}
  \resumeSubHeadingListStart
 
    \resumeSubheading
      {University of Waterloo and Wilfrid Laurier's Double Degree Club}{Waterloo, ON}
      {Director of Finance and Internal Affairs}{January 2021 - April 2021}
        \begin{itemize}
            \item Keeping an up-to-date record, in Excel, of all the transactions made and the purpose of all expenditures.
            \item Maintaining detailed financial records and handing club reimbursements.
            \item Constructing a budget to be approved by Mathsoc and Laurier SU, and adhered to by the club for the term.
        \end{itemize}

    \resumeSubheading
    {Y.M.C.A}{Toronto, ON}
    {Newcomer Youth Leadership Development Mentor} {September 2019 - July 2020}
        \begin{itemize}
            \item Responsible for tutoring and mentoring newcomers and at-risk youth. 
            \item In-charge of planning and directing company events, including budgeting and venue sourcing. 
        \end{itemize}

    

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\shorterSection{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Bachelor of Mathematical Economics }{Expected Graduation: 2024}
      \vspace{-10pt}


\end{document}
